Extracting Function Signature from R Program Traces

### 2020-05-13 paper/main.tex

We contended with multiple type language designs, and in this section we will explore in more detail how we compared our candidate designs.
We will also discuss a large-scale evaluation of our final set of type annotations.

%
%
%
%
\subsection{Comparative Analyses}

\AT{We compared different designs: with/out structs and tuples, with/out classes, with/out primitive subtyping. We looked at type sizes and determined that e.g. \code{? T} is a good type.}

@@

\subsection{Future Work}

>>>>

To evaluate the effectiveness of our type annotation language and contract checking framework, we conducted a large-scale experiment based on the packages we used to inform our language design.
The core corpus of 412 packages represents some of the most widely used and thoroughly tested R libraries on CRAN.
To conduct the evaluation in this section, we configured \typetracer to infer the types of each of the functions that are visible to package clients.
\typetracer inferred these types based on the package text, example, and vignette code.
This section is divided in two parts:
First, we present general information about the generated types, and about the core analysis corpus, and next we discuss an evaluation of the inferred types against the reverse-dependencies (read: clients) of the corpus we analyzed.

%
%
%
%
\subsection{Language Statistics}

\AT{Let's talk about some of the data related to our types themselves.
How many types?
How big are they?
How many are mono? Poly?
Stuff like that.}

@@

%
%
%
%
\subsection{Future Work}

%
%
\subsubsection{Object Orientation in R}

%
%
\subsubsection{Types for Data Frames}

% ======================================
%
% End
%
%
